Reliable error estimation for Sobol' indices

### 2016-03-10 replicated_sobol.tex
Adding definition of replicated digital net

Our goal is to generate two sequences $\{\vx_i\}_{i\in\mathbb{N}_0}$ and $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ such that for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$. For that purpose, $C_j'$ depend on the choice of $C_j$.

Although the choices of $C_j$ and $C_j'$ are many, there is a special case interesting for its construction simplicity, and with a wide range of possible $C_j'$ choices given $C_j$.

Considering the generating matrices to be upper triangular full rank (no zeros on the diagonal), one ensures that $x_{i,j,k}=0$, for $k>m$ and $b^m-1\geq i \geq 0$. Since the block $C_j^{m\times m}$ is full rank, each $x_{i,j}\neq x_{r,j}$ when $i\neq j$. Therefore, excluding the case ${\vx}_i={\vx'}_i$ for all $i\in\mathbb{N}_0$, it is enough to choose $C_j\neq C_j'$ for at least one dimension $j$. When $b=2$, this is the case of Sobol' sequences and one could simply consider $C_{j+d},\dots,C_{2d}$ to generate the replicated sequence.

@@

\subsection{Owen Scrambling To The New Sequence}

>>>>

\subsection{Replicated Digital Sequences}
Here recall the link with the replicated method....
\begin{defin}
A digital sequence $\{{\vx'}_i\}_{i\in\mathbb{N}_0}$ is the replicated digital sequence of $\{\vx_i\}_{i\in\mathbb{N}_0}$ if for all $m\geq 0$, $\{{\vx'}_i\}_{i=0}^{b^m-1}$ is a replicated design of $\{{\vx}_i\}_{i=0}^{b^m-1}$.
\end{defin}
In this case, $C_j'$ will depend on the choice of $C_j$.

Although the choices of $C_j$ and $C_j'$ are many, there is a special case interesting for its construction simplicity, and wide range of $C_j'$ choices.

Considering the generating matrices to be upper triangular and without zeros on the diagonal, one ensures that $x_{i,j,k}=0$, for $m<k$ and $0 \leq i \leq b^m-1$. Since the block $C_j^{m\times m}$ is full rank, each $x_{i,j}\neq x_{r,j}$ when $i\neq j$. Therefore, excluding the case ${\vx}_i={\vx'}_i$ for all $i\in\mathbb{N}_0$, it is enough to choose $C_j\neq C_j'$ for at least $d-1$ dimension. When $b=2$, this is the case of Sobol' sequences and one could simply consider $C_{j+d},\dots,C_{2d}$ to generate the replicated sequence.

@@

\subsection{Owen Scrambling To Replicated Digital Sequences}
